---
title: "ICT_analyses"
output: html_document
---

# R environment & data files

## Required packages

```{r message=FALSE}
required.packages <- c("BayesFactor", "nlme", "plyr", "here", "data.table", "reshape2", "lme4", "dplyr","ggplot2", "ggpubr")

new.packages <- required.packages[!(required.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)>0) {install.packages(new.packages)}

require(BayesFactor)
require(nlme)
require(plyr)
require(here)
require(data.table)
require(reshape2)
require(lme4)
require(dplyr)
require(ggplot2)
require(ggpubr)
```

## Import data files

* All raw data files can be downloaded from the OSF project 'ICT_data' component, available at https://osf.io/9cu64/. Raw data are saved in the 'raw_data.zip'.

* After you have downloaded all files as a zip folder, you can extract this in the 'data' folder for this R project directory. 

* Please note that the csv files are large (10-11 MB) and certain pre-processing steps may take a few minutes to finish. 

* A summary file with the participants' demographics has not been shared as some variables (in combination) may be considered _indirect_ personal identifiers.

* I have manually removed the data files from excluded participants based on the following criteria: 
  - psychiatric/neurological disorders
  - binge eating disorder 
  - drug and/or alcohol abuse
  
```{r}
#Save names from complete data files in the 'data' folder 
files <- list.files(here("data"), all.files = TRUE, full.names = FALSE, no.. = TRUE, pattern = "\\.csv$")

#Make a list of all data files
data <- lapply(here("data", files), function(x) {fread(x)})

#Change structure of files into data frames
data <- lapply(data, function(x) as.data.frame(x))

#Assign names to the list elements (subject IDs)
subs <- lapply(data, function(x) head(x$ID, n=1))
subs <- lapply(subs, function(x) as.character(x))
names(data) <- subs
```

## Load script with functions

```{r}
source("ICT_functions.R")
```

# Data pre-processing 

## Data transformations

* Data were collected in both laboratory and online settings and therefore mouse coordinates correspond to different display resolutions. 

* For this reason, x-y coordinates will be transformed into a standardised space compatible with the aspect ratio used for the experimental task window (2 x 1.5).

* For mouse-tracking analyses, the x-axis should be mapped as [-1, 1] but we prefer to avoid negative values for our calculations and therefore use the [0, 2].

* This transformation will only be applied to data from the training task and go tests. 

* Mouse coordinates from the explicit evaluation task (EET) will undergo a different transformation.

```{r}
#For the following pre-processing steps, we only use the training and go test data. 
#Therefore we create a copy of the 'data' list and name it 'ICT_data' from which only the relevant blockcodes are used.

ICT_data <- lapply(data, subset, block!="tastiness" & block!="desiretoeat" & block!="dummy_taste" & block!="dummy_des")

ICT_data <- lapply(ICT_data, transform, mousex = ifelse(mousex<0, 0, ifelse(mousex>canvas_width, canvas_width, mousex)))


#Apply 'transform_xy' function to ICT_data

ICT_data <- lapply(ICT_data, function(x) transform_xy(min_x = 0, max_x = as.numeric(x$canvas_width), min_y = 0, max_y = as.numeric(x$canvas_height), x = x$mousex, y = x$mousey, data= x))
```

## Trial-to-trial mouse movements

* Information about trial-to-trial mouse movements is obtained, such as previous and next x-y coordinates and the euclidean distance travelled with the mouse from one trial to another (movedXY)

* Reaction times are also recorded on following trials, i.e., rt_sample1: RT before two samples and rt_sample2: RT before eleven samples - these will be necessary for registering RT measures (e.g., SSRT)

* Stopping of the mouse is registered when for 3 or more samples there is no change in mouse coordinates including the pixel tolerance which was set as 20px to account for natural movements of the mouse.

* Stopping for stop-signal trials is registered when for 12 or more samples there is no change in mouse coordinates including the tolerance for natural mouse movements. 

* For RT measures, the first sample of these observations is used as the time-point of interest. 

* It should be noted that change in x-y coordinates was not properly defined. It is crucial to use the euclidean distance to take into account movements in both x and y axes. 

* Importantly, the pixel tolerance of 20px cannot be translated into the transformed x-y coordinates and should not be generalised to different display resolutions (if coordinates were not transformed).

* For that reason, we set a minimum tolerance of 0.01 for movements in the standardised coordinate space. 

```{r}
#Apply 'movements' function to ICT_data to obtain the following measures:

#previous & next x-y coordinates
#movedXY:   Euclidean distance covered with the mouse on a frame-by-frame basis
#rtample1:  reaction time before two samples (frames)
#rtsample2: reaction time before eleven samples 

ICT_data <- lapply(ICT_data, function(x) movements(x$newx, x$newy, x$total_rt,  x))

#Record when stopping occurs including the tolerance of 0.01
ICT_data <- lapply(ICT_data, transform, stopping = ifelse(movedXY <=0.01, 1, 0))

#For accuracy and RTs in no-signal trials we only record stopping when the target has been reached
ICT_data <- lapply(ICT_data, transform, go_stop = ifelse(movedXY <=0.01 & target_reached>0, 1, 0))

#Remove NAs from the vector to avoid errors in applying the function below
ICT_data <- lapply(ICT_data, transform, stopping = ifelse(is.na(stopping), 0, stopping))

#Every time stopping occurs we start recording samples (1, 2, 3, ..), which are reset to 0 when stopping is no longer observed 
ICT_data <- lapply(ICT_data, transform, sample = ave(stopping, cumsum(stopping==0), FUN=cumsum))

ICT_data <- lapply(ICT_data, transform, go_sample = ave(go_stop, cumsum(target_reached==0), FUN=cumsum))
```

## Recode accuracy for no-signal trials

* The code for the experiment did not account for certain responses (e.g., participants reaching both target and non-target) 

* We create another variable for accuracy (ns_accuracy) to record all possible responses:

  -  ns_accuracy==1: correct target was reached on time
  -  ns_accuracy==2: wrong target was reached on time
  -  ns_accuracy==3: participants did not respond on time
  -  ns_accuracy==4: both target and non-target stimuli were reached on time
  
```{r}
#We save accuracy values on the last trial frame (i.e., values.frame_go==112)
ICT_data <- lapply(ICT_data, transform, ns_accuracy = ifelse(target_reached>0 & nontarget_reached==0 & frame_go==106, 1,                   
                                                      ifelse(target_reached==0 & nontarget_reached>0 & frame_go==106, 2, 
                                                      ifelse(target_reached==0 & nontarget_reached==0 & frame_go==106, 3,
                                                      ifelse(target_reached>0 & nontarget_reached>0 & frame_go==106, 4, 0)))))
```

## Split data into groups

> Group 1 = Go (control)
  Group 2 = Stop
  Group 3 = Stop-change

```{r}
#Split list of dataframes into groups and get training data

group1 <- ICT_data[sapply(ICT_data, function(x) all(x$group == 1))]
group2 <- ICT_data[sapply(ICT_data, function(x) all(x$group == 2))]
group3 <- ICT_data[sapply(ICT_data, function(x) all(x$group == 3))]

#Remove columns that we don't need for confirmatory analyses

group1 <- lapply(group1, subset, select=c(1:8, 25:26, 30:34, 36:39, 40:45, 51, 59:66))
group2 <- lapply(group2, subset, select=c(1:8, 25:26, 30:34, 36:39, 40:45, 51, 59:66))
group3 <- lapply(group3, subset, select=c(1:8, 25:26, 30:34, 36:39, 40:45, 51, 59:66))

group1_train <- lapply(group1, subset, block=="go_training")
group2_train <- lapply(group2, subset, block=="stop_training")
group3_train <- lapply(group3, subset, block=="change_training")
```

> Registration of GoRTs

* GoRTs need to be defined according to the new stopping registration we employed with transformed x-y coordinates.

* We will select the first sample out of three in which stopping occured for a CORRECT response.

* In some cases, stopping can be observed more than once during the trial. For this reason, we record the trialcode values of preceding rows and select the first stopping occurence. 

## Data exclusions for GO group 

* Proportion of correct responses in go trials < 85%
* Mean GoRT in go trials >= 3 SDs from training group mean 

```{r}
#Keep trials where stopping occured and the last frames of no-signal and signal trials (both go trials in the GO group)
group1_train <- lapply(group1_train, subset, (go_sample==3 & trial!="mask" & go_stop==1) | frame_go==106 | frame_signal==106)

#Register accuracy for all trials
group1_train <- lapply(group1_train, transform, ns_accuracy = ifelse(target_reached>0 & nontarget_reached==0 & frame_signal==106, 1, 
                    ifelse(target_reached==0 & nontarget_reached>0 & frame_signal==106, 2, 
                    ifelse(target_reached==0 & nontarget_reached==0 & frame_signal==106, 3,
                    ifelse(target_reached>0 & nontarget_reached>0 & frame_signal==106, 4, ns_accuracy)))))

#Record preceding trial and register GoRTs at the last samples (frame_go or frame_signal = 106)
group1_train <- lapply(group1_train, transform, lag_trial = as.character(lag(trial, 1)))

group1_train <- lapply(group1_train, transform, GoRT = if_else(frame_go==106 & (lag_trial=="ns_left"|lag_trial=="ns_right"),lag(rt_sample1, 1), if_else(frame_signal==106 & (lag_trial=="gs_left"|lag_trial=="gs_right"),lag(rt_sample1, 1), 0)))
        
group1_train <- lapply(group1_train, subset, frame_go==106 | frame_signal==106)

#Change NAs into 0s
group1_train <- lapply(group1_train, transform, GoRT = if_else(is.na(GoRT), 0, GoRT))

#Recode accuracy for mean calculation
group1_train <- lapply(group1_train, transform, accuracy=as.numeric(ifelse(ns_accuracy==1, "1", "0")))

# Get mean proportions of correct responses 
group1_means <- ldply(group1_train, function(x) c(goPC= mean(x$accuracy), goRT = mean(x$GoRT[x$accuracy==1])))

#Exclude participants with a proportion of correct responses less than 0.85
group1_means <- subset(group1_means, goPC>=0.85)

#Calculate max based on >3 SDs from group mean
group1_max = mean(group1_means$goRT) + (3 * sd(group1_means$goRT))
```

## Data exclusions for STOP group

* Proportion of correct responses in go trials < 85%
* Proportion of correct responses in stop trials < 65% 
* Mean GoRT in go trials < 3 SDs from training group mean 
* Mean SSRT in stop trials < 2 SDs from the training group mean

```{r}
#Register the RT when the signal-onset distance was reached (i.e., signal onset time). 
group2_train <- lapply(group2_train, transform, signalonset = ifelse(trial=="inter_ss_left"|trial=="inter_ss_right", lead(total_rt, 1)-latency, 0))

#Subset data to keep only relevant trials.
group2_train <- lapply(group2_train, subset, (sample==12 & (trial=="post_ss_left" | trial=="post_ss_right")) | frame_go==106 | frame_signal==106 | (go_sample==3 & (trial=="ns_left"|trial=="ns_right") & go_stop==1) | (trial=="inter_ss_left"|trial=="inter_ss_right"))

# Create variable 'signal' with two levels: ns and ss for no-signal and stop-signal trials respectively
group2_train <- lapply(group2_train, transform, signal = as.factor(if_else(frame_go>0, "ns", "ss")))

# Before we code accuracy for signal trials we need to create a new variable for the side of the screen on which the mouse was when stopping occured
group2_train <- lapply(group2_train, transform, side = as.factor(if_else(newx<0.9, "left", if_else(newx>1.1, "right", "middle"))))

# Create a lag trial
group2_train <- lapply(group2_train, transform, lag_trial = as.character(lag(trial, 1)))

# Direction coding
group2_train <- lapply(group2_train, transform,
  direction = as.factor(if_else((trial=="post_ss_left"|trial=="inter_ss_left") & side != "right", "correct",
    if_else((trial=="post_ss_right"|trial=="inter_ss_right") & side != "left", "correct", if_else(trial == "ns_left" | trial == "ns_right", "nan", "incorrect")))))

# Based on previous trials, we need to categorise the number of stops that occur after signal onset and before the target is reached. 

group2_train <- lapply(group2_train, transform, stop_trial = as.numeric(if_else(trial=="post_ss_left"|trial=="post_ss_right", "1", "0")))

group2_train <- lapply(group2_train, transform, stop_sample = ave(stop_trial, cumsum(stop_trial==0), FUN=cumsum))

# Register GoRTs and accuracy

group2_train <- lapply(group2_train, transform, GoRT = if_else(frame_go==106 & (lag_trial=="ns_left"|lag_trial=="ns_right"),lag(rt_sample1, 1), 0))

group2_train <- lapply(group2_train, transform, lead_trial = as.character(lead(trial, 1)))

group2_train <- lapply(group2_train, transform, 
                       ss_accuracy = ifelse(target_reached==0 & nontarget_reached==0  & direction=="correct" & sample>=12, 1, 0))

#Select only first point of stopping that was observed (stop_sample = 1)
group2_train <- lapply(group2_train, subset, (trial=="inter_ss_left"|trial=="inter_ss_right") | lead(frame_signal,1)==106  | frame_signal==106 | frame_go==106)

group2_train <- lapply(group2_train, transform, ss_accuracy = ifelse(frame_signal=="106", lag(ss_accuracy,1), ss_accuracy))

group2_train <- lapply(group2_train, transform, signalonset = if_else(trial=="post_ss_left"|trial=="post_ss_right", lag(signalonset, 1), signalonset))

group2_train <- lapply(group2_train, transform, signalonset = if_else(frame_signal==106 & (lag_trial=="post_ss_left"|lag_trial=="post_ss_right"), lag(signalonset, 1), signalonset))

group2_train <- lapply(group2_train, transform, stopRT = if_else(stop_sample>=1 & frame_signal!=106, rt_sample2, 0))

group2_train <- lapply(group2_train, transform, SSRT = rt_sample2 - signalonset)
group2_train <- lapply(group2_train, transform, SSRT = if_else(frame_signal==106, lag(SSRT, 1), if_else(stop_sample==1, SSRT, 0)))

#Group 2 descriptives for exclusions

group2_train <- lapply(group2_train, subset, frame_go==106 |frame_signal==106)
group2_train <- lapply(group2_train, transform, GoRT = if_else(is.na(GoRT), 0, GoRT))
group2_train <- lapply(group2_train, transform, SSRT = if_else(is.na(SSRT), 0, SSRT))

group2_train <- lapply(group2_train, transform, ns_accuracy=as.numeric(ifelse(ns_accuracy==1, "1", "0")))
group2_train <- lapply(group2_train, transform, ss_accuracy=as.numeric(ifelse(ss_accuracy==1, "1", "0")))

group2_means <- ldply(group2_train, function(x) c(goPC= mean(x$ns_accuracy[x$signal=="ns"]), stopPC = mean(x$ss_accuracy[x$signal=="ss"]),
                                                  goRT = mean(x$GoRT[x$signal=="ns" & x$ns_accuracy==1]), SSRT = mean(x$SSRT[x$signal=="ss" & x$ss_accuracy==1])))

# Note that accuracy-based exclusions are applied first and then RT-related criteria are checked.
group2_incl_pc_ns <- unique(group2_means$.id[group2_means$goPC>=0.85])

group2_max_ns = mean(group2_means$goRT) + (3 * sd(group2_means$goRT))

group2_incl_rts_ns <- unique(group2_means$.id[group2_means$goRT<group2_max_ns])

group2_means <- subset(group2_means, .id %in% group2_incl_pc_ns)

group2_incl_pc_ss <- unique(group2_means$.id[group2_means$stopPC>=0.65])

group2_means <- subset(group2_means, .id %in% group2_incl_pc_ss)

group2_max_ss = mean(group2_means$SSRT) + (2 * sd(group2_means$SSRT))

group2_incl_rts_ss <- unique(group2_means$.id[group2_means$SSRT<group2_max_ss])
```

## Data exclusions for CHANGE group

* Proportion of correct responses in go trials < 85%
* Proportion of correct responses in stop-change trials < 50% 
* Mean GoRT in go trials < 3 SDs from training group mean 
* Mean CSRT in stop-change trials < 3 SDs from training group mean

```{r}
#Register the RT when the signal-onset distance was reached (i.e., signal onset time). 
group3_train <- lapply(group3_train, transform, signalonset = ifelse(trial=="inter_cs_left"|trial=="inter_cs_right", lead(total_rt, 1)-latency, 0))

#Subset data to keep only relevant trials.
group3_train <- lapply(group3_train, subset, (change==1 & (trial=="post_cs_left" | trial=="post_cs_right")) | frame_go==106 | frame_signal==106 | (go_sample==3 & (trial=="ns_left"|trial=="ns_right") & go_stop==1) | (trial=="inter_cs_left"|trial=="inter_cs_right"))

#Record change samples
group3_train <- lapply(group3_train, transform, change= as.numeric(ifelse(frame_signal==106, "0", change)))

group3_train <- lapply(group3_train, transform, change_sample = ave(change, cumsum(change==0), FUN=cumsum))

group3_train <- lapply(group3_train, subset, change_sample=="3" | (go_sample==3 & (trial=="ns_left"|trial=="ns_right") & go_stop==1) | (trial=="inter_cs_left"|trial=="inter_cs_right") | frame_go==106 | frame_signal==106)

#Create variable 'signal' with two levels: ns and ss for no-signal and change-signal trials respectively
group3_train <- lapply(group3_train, transform, signal = as.factor(if_else(frame_go>0, "ns", "ss")))

#Calculate the change-signal reaction time (CSRT)
group3_train <- lapply(group3_train, transform, lag_trial = as.character(lag(trial, 1)))

group3_train <- lapply(group3_train, transform, CSRT = if_else(frame_signal==106 & (lag_trial=="post_cs_left"|lag_trial=="post_cs_right"), lag(rt_sample1, 1), 0))

group3_train <- lapply(group3_train, transform, signalonset = if_else((trial=="post_cs_left"|trial=="post_cs_right"), lag(signalonset, 1), signalonset))

group3_train <- lapply(group3_train, transform, signalonset = if_else((lag_trial=="post_cs_left"|lag_trial=="post_cs_right"), lag(signalonset, 1), signalonset))

group3_train <- lapply(group3_train, transform, CSRT = as.numeric(CSRT - signalonset))

#Define accuracy for change-signal trials
group3_train <- lapply(group3_train, transform, sc_accuracy = if_else(frame_signal==106 & target_reached==0 & nontarget_reached>0 & correct_direction1==1, 1, 0))

#Get GoRTs from no-signal trials
group3_train <- lapply(group3_train, transform, GoRT = if_else(frame_go==106 & (lag_trial=="ns_left"|lag_trial=="ns_right"), lag(rt_sample1, 1), 0))

#Group 3 descriptives for exclusions

group3_train <- lapply(group3_train, subset, frame_go==106 |frame_signal==106)
group3_train <- lapply(group3_train, transform, GoRT = if_else(is.na(GoRT), 0, GoRT))
group3_train <- lapply(group3_train, transform, CSRT = if_else(is.na(CSRT), 0, CSRT))

group3_train <- lapply(group3_train, transform, ns_accuracy=as.numeric(ifelse(ns_accuracy==1, "1", "0")))
group3_train <- lapply(group3_train, transform, sc_accuracy=as.numeric(ifelse(sc_accuracy==1, "1", "0")))

group3_means <- ldply(group3_train, function(x) c(goPC= mean(x$ns_accuracy[x$signal=="ns"]), changePC = mean(x$sc_acc[x$signal=="ss"]),
                                                  goRT = mean(x$GoRT[x$signal=="ns" & x$ns_accuracy==1]), CSRT = mean(x$CSRT[x$signal=="ss" & x$sc_accuracy==1])))

#Subset datasets for participants who do not meet the exclusion criteria
group3_incl_pc_ns <- unique(group3_means$.id[group3_means$goPC>=0.85])

group3_max_ns = mean(group3_means$goRT) + (3 * sd(group3_means$goRT))

group3_means <- subset(group3_means, .id %in% group3_incl_pc_ns)

group3_incl_pc_ss <- unique(group3_means$.id[group3_means$changePC>=0.50])

group3_means <- subset(group3_means, .id %in% group3_incl_pc_ss)

group3_max_ss = mean(group3_means$CSRT) + (3 * sd(group3_means$CSRT))

group3_incl_rts_ns <- unique(group3_means$.id[group3_means$goRT<group3_max_ns])
group3_incl_rts_ss <- unique(group3_means$.id[group3_means$CSRT<group3_max_ss])
```

## Apply exclusions to all data

```{r}
group1_include <- unique(group1_means$.id[group1_means$goRT < group1_max])

group2_include <- unique(group2_means$.id[group2_means$goRT<group2_max_ns & group2_means$SSRT<group2_max_ss])

group3_include <- unique(group3_means$.id[group3_means$goRT<group3_max_ns & group3_means$CSRT<group3_max_ss])

#Clear datasets 

group1 <- group1[sapply(group1, function(x) any(x$ID %in% group1_include))]
group2 <- group2[sapply(group2, function(x) any(x$ID %in% group2_include))]
group3 <- group3[sapply(group3, function(x) any(x$ID %in% group3_include))]

group1_train <- group1_train[sapply(group1_train, function(x) any(x$ID %in% group1_include))]
group2_train <- group2_train[sapply(group2_train, function(x) any(x$ID %in% group2_include))]
group3_train <- group3_train[sapply(group3_train, function(x) any(x$ID %in% group3_include))]

groups_include <- c(group1_include, group2_include, group3_include)

ICT_data <- ICT_data[sapply(ICT_data, function(x) any(x$ID %in% groups_include))]
data <- data[sapply(data, function(x) any(x$ID %in% groups_include))]
```

## Evaluation task data

```{r}
#Record minimum and maximum y coordinates based on the task (canvas) window
data <- lapply(data, transform, y_min = ((canvas_height * 0.07) - (canvas_height * 0.04)/2))
data <- lapply(data, transform, y_max = ((canvas_height * 0.07) + (canvas_height * 0.04)/2))

#Register stopping on EET trials (>= 3 samples)
data <- lapply(data, transform, prevx = lag(mousex, 1))
data <- lapply(data, transform, prevy = lag(mousey, 1))

data <- lapply(data, transform, stopping = if_else(mousex==prevx & mousey==prevy, 1, 0))

data <- lapply(data, subset, trial!="post_practice")

data <- lapply(data, transform, sample = ave(as.numeric(stopping), cumsum(stopping==0), FUN=cumsum))
data <- lapply(data, transform, eval_stop = if_else(sample==3 & init_time > 0 & (block=="desiretoeat"|block=="tastiness"), 2, 0))

#Code accuracy of coordinates- i.e., if they are in the accepted range for VAS or not
data <- lapply(data, transform, cor_xy = if_else(mousey>=y_min & mousey <= y_max & mousex>=min_eval & mousex <= max_eval, 1, 0))

#Two participants were found to respond on EET trials by simply moving their mouse to the VAS and waiting for the next trial. Since they did not click on the VAS for their responses to be registered, I have manually coded when the mouse cursor was within the acceptable VAS x-y coordinates and they stopped moving their mouse for at least 3 samples

data$`283948702_2_14_57_20`$marker = ifelse(data$`283948702_2_14_57_20`$eval_stop==2 & data$`283948702_2_14_57_20`$cor_xy==1, 2, 0)

data$`701639649_2_15_07_36`$marker = ifelse(data$`701639649_2_15_07_36`$eval_stop==2 & data$`701639649_2_15_07_36`$cor_xy==1, 2, 0)
  
#Subset all data to only include completed EET responses
des <- lapply(data, subset, block=="desiretoeat" & marker==2)
tas <- lapply(data, subset, block=="tastiness" & marker==2)

#A few participants in the beginning of data collection had duplicate jpgs appearing (extra trials) due to an error in the experimental scripts. This issue is corrected by removing the duplicates.
des <- lapply(des, function(x) rm_d(x))
tas <- lapply(tas, function(x) rm_d(x))

#Coordinate log transformation for EET responses

des$`283948702_2_14_57_20`$markerx <- des$`283948702_2_14_57_20`$mousex
tas$`283948702_2_14_57_20`$markerx <- tas$`283948702_2_14_57_20`$mousex

des$`701639649_2_15_07_36`$markerx <- des$`701639649_2_15_07_36`$mousex
tas$`701639649_2_15_07_36`$markerx <- tas$`701639649_2_15_07_36`$mousex

des <- lapply(des, function(x) transform_x(x$min_eval, x$max_eval, x$markerx, x))
tas <- lapply(tas, function(x) transform_x(x$min_eval, x$max_eval, x$markerx, x))

#Change the names and structure of variables to be included in later analyses
tas <- lapply(tas, transform, healthiness = as.factor(eval_healthiness))
tas <- lapply(tas, transform, novelty = as.factor(eval_novelty))
tas <- lapply(tas, transform, selection = as.factor(eval_selection))
tas <- lapply(tas, transform, item = as.factor(eval_jpg))

des <- lapply(des, transform, healthiness = as.factor(eval_healthiness))
des <- lapply(des, transform, novelty = as.factor(eval_novelty))
des <- lapply(des, transform, selection = as.factor(eval_selection))
des <- lapply(des, transform, item = as.factor(eval_jpg))

#Important: The side on which the positive/negative anchors of the VAS appeared was randomised across participants and therefore coordinates need to remapped so that for all participants the positive end would be on the right side.
tas <- lapply(tas, function(x) cbind(x, xcoord=ifelse(x$eval_side==2, abs(x$newx-100), x$newx)))
des <- lapply(des, function(x) cbind(x, xcoord=ifelse(x$eval_side==2, abs(x$newx-100), x$newx)))

#Split datasets according to healthiness 
tas_h <- lapply(tas, subset, healthiness==1)
tas_u <- lapply(tas, subset, healthiness==2)

des_h <- lapply(des, subset, healthiness==1)
des_u <- lapply(des, subset, healthiness==2)

#Mean ratings for EET data (for each design cell)
tas_us <- ldply(tas_u, eval)
tas_hs <- ldply(tas_h, eval)

des_us <- ldply(des_u, eval)
des_hs <- ldply(des_h, eval)


#Files for JASP
tas_u_stop <- subset(tas_us, Group!=3)
tas_h_stop <- subset(tas_hs, Group!=3)

des_u_stop <- subset(des_us, Group!=3)
des_h_stop <- subset(des_hs, Group!=3)

tas_u_change <- subset(tas_us, Group!=2)
tas_h_change <- subset(tas_hs, Group!=2)

des_u_change <- subset(des_us, Group!=2)
des_h_change <- subset(des_hs, Group!=2)

write.csv(tas_u_stop, file=here("JASP", "tas_u_stop.csv"), row.names = FALSE)
write.csv(tas_h_stop, file=here("JASP", "tas_h_stop.csv"), row.names = FALSE)
write.csv(des_u_stop, file=here("JASP", "des_u_stop.csv"), row.names = FALSE)
write.csv(des_h_stop, file=here("JASP", "des_h_stop.csv"), row.names = FALSE)

write.csv(tas_u_change, file=here("JASP", "tas_u_change.csv"), row.names = FALSE)
write.csv(tas_h_change, file=here("JASP", "tas_h_change.csv"), row.names = FALSE)
write.csv(des_u_change, file=here("JASP", "des_u_change.csv"), row.names = FALSE)
write.csv(des_h_change, file=here("JASP", "des_h_change.csv"), row.names = FALSE)

#Dataframes for model comparisons (BayesFactor package)
tas_h <- ldply(tas_h, as.data.frame)
tas_u <- ldply(tas_u, as.data.frame)

des_h <- ldply(des_h, as.data.frame)
des_u <- ldply(des_u, as.data.frame)

tas_h$ID <- droplevels(as.factor(tas_h$ID))
tas_u$ID <- droplevels(as.factor(tas_u$ID))

des_h$ID <- droplevels(as.factor(des_h$ID))
des_u$ID <- droplevels(as.factor(des_u$ID))

tas_u$group <- as.factor(tas_u$group)
tas_h$group <- as.factor(tas_h$group)

des_u$group <- as.factor(des_u$group)
des_h$group <- as.factor(des_h$group)

#Export data files for OSF
write.csv(tas_h, file=here("OSF_data", "tas_h.csv"), row.names = FALSE)
write.csv(tas_u, file=here("OSF_data", "tas_u.csv"), row.names = FALSE)

write.csv(des_h, file=here("OSF_data", "des_h.csv"), row.names = FALSE)
write.csv(des_u, file=here("OSF_data", "des_u.csv"), row.names = FALSE)
```

## Go test data

```{r}
#We need to get difference scores for goRT (post-pre) from mean GoRTs
go_test <- lapply(ICT_data, subset, block=="go_test" | block=="go_test_end")

go_test <- lapply(go_test, subset, (go_sample==3 & trial!="mask" & go_stop==1) | frame_go==106)

go_test <- lapply(go_test, transform, lag_trial = as.character(lag(trial, 1)))

go_test<- lapply(go_test, transform, GoRT = if_else(frame_go==106 & (lag_trial=="ns_left"|lag_trial=="ns_right"),lag(rt_sample1, 1), 0))
        
go_test <- lapply(go_test, subset, frame_go==106)

go_test <- lapply(go_test, transform, GoRT = if_else(is.na(GoRT), 0, GoRT))

#Recode accuracy for mean calculation
go_test <- lapply(go_test, transform, accuracy=as.numeric(ifelse(ns_accuracy==1, "1", "0")))

#For GoRTs we only consider correct trials
go_test_cor <- lapply(go_test, subset, accuracy==1)

#Apply function for mean GoRTs
go_sum <- ldply(go_test_cor, go_RTs)
go_sum$Group <- as.factor(go_sum$Group)

#Difference scores for pre-post mean GoRTs 

#DGoRT_U: DGoRT for unhealthy foods
#DGoRT_H: DGoRT for healthy foods
#DGoRT_SU: DGoRT for selected unhealthy foods
#DGoRT_NU: DGoRT for non-selected unhealthy foods

go_sum$DGoRT_U = go_sum$GoRT.U.Post - go_sum$GoRT.U.Pre
go_sum$DGoRT_H = go_sum$GoRT.H.Post - go_sum$GoRT.H.Pre

go_sum$DGoRT_SU = go_sum$GoRT.SU.Post - go_sum$GoRT.SU.Pre
go_sum$DGoRT_NU = go_sum$GoRT.NU.Post - go_sum$GoRT.NU.Pre

#Data files for JASP
go_sum_stopgo <- subset(go_sum, Group!="3")
go_sum_changego <- subset(go_sum, Group!="2")


write.csv(go_sum_stopgo, file=here("JASP", "go_sum_stopgo.csv"), row.names = FALSE)
write.csv(go_sum_changego, file=here("JASP", "go_sum_changego.csv"), row.names = FALSE)
```

# Linear mixed-effects models

> Abbreviations for model selection

BTU1 - Bayesian, tastiness ratings, unhealthy foods, model 1
BTU2 - Bayesian, tastiness ratings, unhealthy foods, model 2 [...]  

BDU1 - Bayesian, desire to eat ratings, unhealthy foods, model 1
BTH1 - Bayesian, tastiness ratings, healthy foods, model 1
BDH1 - Bayesian, desire to eat ratings, healthy foods, model 1

Frequentist equivalents:

FTU1, FDU1
FTH1, FDH1

## Bayesian LMMs

```{r}
#Tastiness ratings - unhealthy foods
BTU1 <- lmBF(data=tas_u, xcoord ~ group * selection * novelty +  + item, whichRandom = c("ID", "item"))
BTU2 <- lmBF(data=tas_u, xcoord ~ group * selection + novelty + ID + item, whichRandom = c("ID", "item"))
BTU3 <- lmBF(data=tas_u, xcoord ~ group * selection +  ID + item, whichRandom = c("ID", "item"))
BTU4 <- lmBF(data=tas_u, xcoord ~ group + selection + ID + item, whichRandom = c("ID", "item"))
BTU5 <- lmBF(data=tas_u, xcoord ~ group + ID + item, whichRandom = c("ID", "item"))
BTU6 <- lmBF(data=tas_u, xcoord ~ selection + ID + item, whichRandom = c("ID", "item"))
BTU7 <- lmBF(data=tas_u, xcoord ~ group * novelty + selection + ID + item, whichRandom = c("ID", "item"))
BTU8 <- lmBF(data=tas_u, xcoord ~ group + novelty + selection + ID + item, whichRandom = c("ID", "item"))


#Get ouput for all 'tas_u' models
BTU_all <- c(BTU1, BTU2, BTU3, BTU4, BTU5, BTU6, BTU7, BTU8)
```

```{r}
#Top models
head(BTU_all)@bayesFactor[1]
```


```{r}
#Desire to eat ratings - unhealthy foods
BDU1 <- lmBF(data=des_u, xcoord ~ group * selection * novelty + ID + item, whichRandom = c("ID", "item"))
BDU2 <- lmBF(data=des_u, xcoord ~ group * selection + novelty + ID + item, whichRandom = c("ID", "item"))
BDU3 <- lmBF(data=des_u, xcoord ~ group * selection +  ID + item, whichRandom = c("ID", "item"))
BDU4 <- lmBF(data=des_u, xcoord ~ group + selection + ID + item, whichRandom = c("ID", "item"))
BDU5 <- lmBF(data=des_u, xcoord ~ group + ID + item, whichRandom = c("ID", "item"))
BDU6 <- lmBF(data=des_u, xcoord ~ selection + ID + item, whichRandom = c("ID", "item"))
BDU7 <- lmBF(data=des_u, xcoord ~ group * novelty + selection + ID + item, whichRandom = c("ID", "item"))
BDU8 <- lmBF(data=des_u, xcoord ~ group + novelty + selection + ID + item, whichRandom = c("ID", "item"))

#Get ouput for all 'tas_u' models
BDU_all <- c(BDU1, BDU2, BDU3, BDU4, BDU5, BDU6, BDU7, BDU8)
```

```{r}
#Top models
head(BDU_all)@bayesFactor[1]
```


```{r}
#Desire to eat ratings - unhealthy foods
BTH1 <- lmBF(data=tas_h, xcoord ~ group * selection * novelty + ID + item, whichRandom = c("ID", "item"))
BTH2 <- lmBF(data=tas_h, xcoord ~ group * selection + novelty + ID + item, whichRandom = c("ID", "item"))
BTH3 <- lmBF(data=tas_h, xcoord ~ group * selection +  ID + item, whichRandom = c("ID", "item"))
BTH4 <- lmBF(data=tas_h, xcoord ~ group + selection + ID + item, whichRandom = c("ID", "item"))
BTH5 <- lmBF(data=tas_h, xcoord ~ group + ID + item, whichRandom = c("ID", "item"))
BTH6 <- lmBF(data=tas_h, xcoord ~ selection + ID + item, whichRandom = c("ID", "item"))
BTH7 <- lmBF(data=tas_h, xcoord ~ group * novelty + selection + ID + item, whichRandom = c("ID", "item"))
BTH8 <- lmBF(data=tas_h, xcoord ~ group + novelty + selection + ID + item, whichRandom = c("ID", "item"))

#Get ouput for all 'tas_u' models
BTH_all <- c(BTH1, BTH2, BTH3, BTH4, BTH5, BTH6, BTH7, BTH8)
```

```{r}
#Top models
head(BTH_all)@bayesFactor[1]
```

```{r}
#Desire to eat ratings - unhealthy foods
BDH1 <- lmBF(data=des_h, xcoord ~ group * selection * novelty + ID + item, whichRandom = c("ID", "item"))
BDH2 <- lmBF(data=des_h, xcoord ~ group * selection + novelty + ID + item, whichRandom = c("ID", "item"))
BDH3 <- lmBF(data=des_h, xcoord ~ group * selection +  ID + item, whichRandom = c("ID", "item"))
BDH4 <- lmBF(data=des_h, xcoord ~ group + selection + ID + item, whichRandom = c("ID", "item"))
BDH5 <- lmBF(data=des_h, xcoord ~ group + ID + item, whichRandom = c("ID", "item"))
BDH6 <- lmBF(data=des_h, xcoord ~ selection + ID + item, whichRandom = c("ID", "item"))
BDH7 <- lmBF(data=des_h, xcoord ~ group * novelty + selection + ID + item, whichRandom = c("ID", "item"))
BDH8 <- lmBF(data=des_h, xcoord ~ group + novelty + selection + ID + item, whichRandom = c("ID", "item"))

#Get ouput for all 'tas_u' models
BDH_all <- c(BDH1, BDH2, BDH3, BDH4, BDH5, BDH6, BDH7, BDH8)
```

```{r}
#Top models
head(BDH_all)@bayesFactor[1]
```

## Interaction effects

```{r}
BTU3/BTU4
```

```{r}
FTU3 <- lmer(data=tas_u, xcoord ~ group * selection +  (1|ID) + (1|item))
FTU4 <- lmer(data=tas_u, xcoord ~ group + selection +  (1|ID) + (1|item))

anova(FTU3, FTU4)
```

```{r}
BDU3/BDU4
```
```{r}
FDU3 <- lmer(data=des_u, xcoord ~ group * selection +  (1|ID)+ (1|item))
FDU4 <- lmer(data=des_u, xcoord ~ group + selection +  (1|ID)+ (1|item))

anova(FDU3, FDU4)
```

```{r}
BTH3/BTH4
```

```{r}
FTH3 <- lmer(data=tas_h, xcoord ~ group * selection +  (1|ID)+ (1|item))
FTH4 <- lmer(data=tas_h, xcoord ~ group + selection +  (1|ID)+ (1|item))

anova(FTH3, FTH4)
```

```{r}
BDH3/BDH4
```

```{r}
FDH3 <- lmer(data=des_h, xcoord ~ group * selection +  (1|ID)+ (1|item))
FDH4 <- lmer(data=des_h, xcoord ~ group + selection +  (1|ID)+ (1|item))

anova(FDH3, FDH4)
```

* Three-way interaction vs only additive effect of novelty
```{r}
BTU1 / BTU2
```

```{r}
FTU1 <- lmer(data=tas_u, xcoord ~ group * selection * novelty +  (1|ID)+ (1|item))
FTU2 <- lmer(data=tas_u, xcoord ~ group * selection + novelty +  (1|ID)+ (1|item))

anova(FTU1, FTU2)
```

```{r}
BTH1 / BTH2
```

```{r}
FTH1 <- lmer(data=tas_h, xcoord ~ group * selection * novelty +  (1|ID)+ (1|item))
FTH2 <- lmer(data=tas_h, xcoord ~ group * selection + novelty +  (1|ID)+ (1|item))

anova(FTH1, FTH2)
```

```{r}
BDU1 / BDU2
```

```{r}
FDU1 <- lmer(data=des_u, xcoord ~ group * selection * novelty +  (1|ID)+ (1|item))
FDU2 <- lmer(data=des_u, xcoord ~ group * selection + novelty +  (1|ID)+ (1|item))

anova(FDU1, FDU2)
```

```{r}
BDH1 / BDH2
```

```{r}
FDH1 <- lmer(data=des_h, xcoord ~ group * selection * novelty +  (1|ID)+ (1|item))
FDH2 <- lmer(data=des_h, xcoord ~ group * selection + novelty +  (1|ID)+ (1|item))

anova(FDH1, FDH2)
```

## Model diagnostic plots [optional]

```{r}
ggplot(FTU1, aes(y= residuals(FTU1), x=fitted.values(FTU1))) + geom_point(size=1, colour="blue", shape=19, alpha=0.15) + 
  geom_hline(yintercept=0, alpha=0.4) + theme_minimal_grid(font_size = 15, font_family = "Palatino") +
  xlab("\nFitted values") + ylab("Residuals\n") + ggplot2::ggtitle(expression("Full model for evaluations"["unhealthy"]))

ggsave("ftu1.fitted.png", dpi=300, height=5, width = 7)

ggplot(FTU1, aes(resid(FTU1))) + geom_density(alpha=.2, fill="blue") + theme_minimal_grid(font_size = 15, font_family = "Palatino") + ylab("Density\n") + xlab("\nResiduals")+    stat_function(fun = dnorm, args = list(mean = mean(resid(FTU1)), sd = sd(resid(FTU1))), color="red", size=1)

ggsave("ftu1.norm.png", dpi=300, height=5, width = 7)

ggplot(FTH1, aes(y= residuals(FTH1), x=fitted.values(FTH1))) + geom_point(size=1, colour="purple", shape=19, alpha=0.15) + 
  geom_hline(yintercept=0, alpha=0.4) + theme_minimal_grid(font_size = 15, font_family = "Palatino") +
  xlab("\nFitted values") + ylab("Residuals\n") + ggplot2::ggtitle(expression("Full model for evaluations"["healthy"]))

ggsave("fth1.fitted.png", dpi=300, height=5, width = 7)

ggplot(FTH1, aes(resid(FTH1))) + geom_density(alpha=.2, fill="purple") + theme_minimal_grid(font_size = 15, font_family = "Palatino") + ylab("Density\n") + xlab("\nResiduals")+    stat_function(fun = dnorm, args = list(mean = mean(resid(FTH1)), sd = sd(resid(FTH1))), color="red", size=1)

ggsave("fth1.norm.png", dpi=300, height=5, width = 7)


ggplot(FDU1, aes(y= residuals(FDU1), x=fitted.values(FDU1))) + geom_point(size=1, colour="magenta", shape=19, alpha=0.15) + 
  geom_hline(yintercept=0, alpha=0.4) + theme_minimal_grid(font_size = 15, font_family = "Palatino") +
  xlab("\nFitted values") + ylab("Residuals\n") + ggplot2::ggtitle(expression("Full model for cravings"["unhealthy"]))

ggsave("fdu1.fitted.png", dpi=300, height=5, width = 7)

ggplot(FDU1, aes(resid(FDU1))) + geom_density(alpha=.2, fill="magenta") + theme_minimal_grid(font_size = 15, font_family = "Palatino") + ylab("Density\n") + xlab("\nResiduals")+    stat_function(fun = dnorm, args = list(mean = mean(resid(FDU1)), sd = sd(resid(FDU1))), color="red", size=1)

ggsave("fdu1.norm.png", dpi=300, height=5, width = 7)


ggplot(FDH1, aes(y= residuals(FDH1), x=fitted.values(FDH1))) + geom_point(size=1, colour="darkorange", shape=19, alpha=0.15) + 
  geom_hline(yintercept=0, alpha=0.4) + theme_minimal_grid(font_size = 15, font_family = "Palatino") +
  xlab("\nFitted values") + ylab("Residuals\n") + ggplot2::ggtitle(expression("Full model for cravings"["healthy"]))

ggsave("fdh1.fitted.png", dpi=300, height=5, width = 7)

ggplot(FDH1, aes(resid(FDH1))) + geom_density(alpha=.2, fill="darkorange") + theme_minimal_grid(font_size = 15, font_family = "Palatino") + ylab("Density\n") + xlab("\nResiduals")+    stat_function(fun = dnorm, args = list(mean = mean(resid(FDH1)), sd = sd(resid(FDH1))), color="red", size=1)

ggsave("fdh1.norm.png", dpi=300, height=5, width = 7)

```



